---
title: "obesity model"
author: "XXX"
date: "2024"
output:
  html_notebook: 
    highlight: tango
    theme: spacelab
    toc: yes
    toc_float: yes
    toc_depth: 5
  html_document:
    df_print: paged
---
## Preparing the R environment
### Set the location of the directory
```{r setup, include=FALSE}
if (!require('knitr')) install.packages('knitr'); library('knitr')
opts_knit$set(root.dir = "...")

knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```


### Import related packages
```{r}

if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse')
if (!require('GGally')) install.packages('GGally'); library('GGally')
if (!require('cowplot')) install.packages('cowplot'); library('cowplot')
if (!require('rpart')) install.packages('rpart'); library('rpart')
if (!require('rpart.plot')) install.packages('rpart.plot'); library('rpart.plot')
if (!require('randomForest')) install.packages('randomForest'); library('randomForest')
if (!require('caret')) install.packages('caret'); library('caret')
if (!require('inspectdf')) install.packages('inspectdf'); library('inspectdf')
if (!require('DMwR2')) install.packages('DMwR2'); library('DMwR2')
if (!require('grid')) install.packages('grid'); library('grid')
```


## Data processing

### Read data set
```{r}
obesity_data <- read.csv("ObesityDataSet.csv")

str(obesity_data)
inspect_types(obesity_data)
```

### Change columns name
```{r}
names(obesity_data) <- c("gender","age","height","weight","fam_history","eat_highcal","vegetables","num_meals","betw_meals","smoke","num_water","monitor_cal","num_exercise","time_devices","num_alcohol","transportation","obe_level")
```



### covert into integer or numeric
```{r}
obesity_data$height <- round(obesity_data$height,2)


cols <- c("age","weight", "vegetables", "num_meals","num_water","num_exercise","time_devices")

for (i in cols){
  obesity_data[,i] <- as.integer(unlist(obesity_data[,i]))
}

```



### define target variables
```{r}
obesity_data <- obesity_data %>% 
  mutate(BMI = round(obesity_data$weight / ((obesity_data$height) ^ 2),1),
         category = case_when(
           BMI < 18.5 ~ "Underweight",
           BMI >= 18.5 & BMI <= 24.9 ~ "Normalweight",
           BMI >= 25.0 & BMI <= 29.9 ~ "Overweight",
           BMI >= 30.0 & BMI <= 34.9 ~ "Obesity_I",
           BMI >= 35.0 & BMI <= 39.9 ~ "Obesity_II",
           BMI >= 40.0 ~ "Obesity_III"))

```




```{r}
inspect_na(obesity_data)
```




```{r}
obesity <- obesity_data %>% 
  select(-obe_level) %>% 
  rename(obe_level = category)
```

```{r}
str(obesity)
```



### variable  recoding
```{r}
obesity$gender <- ifelse(obesity$gender == "Male",2,1)

obesity$fam_history <- ifelse(obesity$fam_history == "yes",2,1)

obesity$eat_highcal <- ifelse(obesity$eat_highcal == "yes",2,1)

obesity$smoke <- ifelse(obesity$smoke == "yes",2,1)

obesity$monitor_cal <- ifelse(obesity$monitor_cal == "yes",2,1)


obesity$betw_meals <- recode(obesity$betw_meals,"no" = 1,
                                                "Sometimes" = 2,
                                                "Frequently" = 3,
                                                "Always" = 4)
 
obesity$num_alcohol <- recode(obesity$num_alcohol,"no" = 1,
                                                  "Sometimes" = 2,
                                                  "Frequently" = 3,
                                                  "Always" = 4)

obesity$transportation <- recode(obesity$transportation,"Bike" = 1,
                                                        "Motorbike" = 2,
                                                        "Automobile" = 3,
                                                        "Public_Transportation" = 4,
                                                        "Walking" = 5)


obesity$obe_level <- recode(obesity$obe_level,"Underweight" = 1,
                                              "Normalweight" = 2,
                                              "Overweight" = 3,
                                              "Obesity_I" = 4,
                                              "Obesity_II" = 5,
                                              "Obesity_III" = 6)
                                              


# change original number

obesity$num_exercise <- recode(obesity$num_exercise,"0" = 1,
                                                    "1" = 2,
                                                    "2" = 3,
                                                      "3" = 4)


obesity$time_devices <- recode(obesity$time_devices,"0" = 1,
                                                     "1" = 2,
                                                     "2" = 3)
                                                 
```



```{r}

inspect_na(obesity)

```


```{r}
inspect_types(obesity)
```

```{r}
str(obesity)
```




```{r}

obesity$gender <- factor(obesity$gender, 
                            levels = c("1", "2"), 
                            labels = c("Female", "Males"))

obesity$fam_history <- factor(obesity$fam_history, 
                               levels = c("1", "2"), 
                               labels = c("No", "Yes"))

obesity$eat_highcal <- factor(obesity$eat_highcal, 
                               levels = c("1", "2"), 
                               labels = c("No", "Yes"))

obesity$betw_meals <- factor(obesity$betw_meals, 
                               levels = c("1", "2","3","4"), 
                               labels = c("No", "Sometimes","Frequently","Always"))


obesity$smoke <- factor(obesity$smoke, 
                               levels = c("1", "2"), 
                               labels = c("No", "Yes"))

obesity$monitor_cal <- factor(obesity$monitor_cal, 
                               levels = c("1", "2"), 
                               labels = c("No", "Yes"))


obesity$num_exercise <- factor(obesity$num_exercise, 
                               levels = c("1", "2","3","4"), 
                               labels = c("I do not have", "1 or 2 days ","2 or 4 days","4 or 5 days"))


obesity$time_devices <- factor(obesity$time_devices, 
                               levels = c("1", "2","3"), 
                               labels = c("0-2 hours", "3-5 hours","more than 5 hours"))


obesity$num_alcohol <- factor(obesity$num_alcohol, 
                               levels = c("1", "2","3","4"), 
                               labels = c("No", "Sometimes","Frequently","Always"))

obesity$transportation <- factor(obesity$transportation, 
                               levels = c("1", "2","3","4","5"), 
                               labels = c("bike", "motorbike","automobile","public transportation","walking"))


obesity$vegetables <- factor(obesity$vegetables, 
                               levels = c("1", "2","3"), 
                               labels = c("never", "Sometimes","Always"))

obesity$num_meals <- factor(obesity$num_meals, 
                               levels = c("1", "2","3","4"), 
                               labels = c("between 1 and 2", "Three","more than 3","no answer"))

obesity$num_water <- factor(obesity$num_water, 
                               levels = c("1", "2","3"),
                               labels = c("less than 1 L", "between 1 and 2L","more than 2L"))


obesity$obe_level <- factor(obesity$obe_level, 
                            levels = c("1", "2", "3","4","5","6"), 
                            labels = c("Underweight", "Normalweight", "Overweight","Obesity_I","Obesity_II","Obesity_III"))
```




```{r}
str(obesity)
```

## Analyse the relationship between variables and obesity

Exploratory data analysis and get a general overview of the variables.

### General overview of the variables

```{r}
summary(obesity)
```

```{r}
inspect_cat(obesity)
```


```{r}
inspect_num(obesity)
```

```{r}
inspect_na(obesity)
```

cheack the number of the obeisty level, and to see  the dataset if it is balanced.
```{r}
obesity %>% 
  count(obe_level)
```

```{r}

ggplot(data = obesity, mapping = aes(x = obe_level, fill = obe_level)) +
  geom_bar() +
  geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5) +  # 在每个柱子上添加文本标签
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())
```



we can see that the distribution of the obesity level is balanced, so we don't need to address the imbalanced class problem.



## Exploryatory analysis
### The gender of a person
Female = 0
male = 1  
```{r}
ggplot(data = obesity, mapping = aes(x= gender, fill = obe_level )) + 
  geom_bar() + 
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())
```
The number of men and women is quite similar.



### The age of a person

```{r}
plot.count <- ggplot(data = obesity,mapping = aes(x= age, fill = obe_level)) + 
              geom_histogram(binwidth = 1) + 
              theme(legend.position = "none",axis.title.x = element_blank(), axis.title.y = element_blank()) 

plot.frequency <- ggplot(data = obesity,mapping = aes(x= age, fill = obe_level)) + 
              geom_histogram(binwidth = 1, position = "fill") + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) 
plot_grid(plot.count,plot.frequency,rel_widths = c(1,1.4))
```
The main number of people surveyed were aged 16-27 and adolescents are prone to obesity.



```{r}
ggplot(obesity, aes(x = obe_level, y = age, fill = obe_level)) +
  geom_boxplot() +
  labs(title = "Age Distribution across Obesity Levels", x = "Obesity Level", y = "Age") +
  theme_minimal()
```

we can see that the boxplot distribution of normal weight and underweight are more concentrated, therefore it can be concluded that Normal Weight  and underweight are mostly concentrated in twenties. 

However, the distribution of the obese group is quite spread out, with the overall distribution being between the ages of 20-30. Therefore, we can say that if people more prone to 30, they are more likely to suffer from obesity.
Among them, obesity_I and overweight have the largest population span, from 20-42 years old.


### The height and weight of a person 

height and weight are in positive relationships

```{r}
ggplot(obesity, aes(x = height,y = weight, color = obe_level)) + 
  geom_point(size = 2, alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE, linetype = "solid", color = "black") +
  labs(x = "Height",y = "Weight", color = "Obesity level") + 
  ggtitle("Relationship between Height, Weight, and Obesity Level") 
```



### If a family member has experienced or currently experiences issues with being overweight?

```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= fam_history, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) + 
              ggtitle("Family history of obesity")
              
plot.count


```
most of people have obesity family history.



### If consume high-calorie food 
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= eat_highcal, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) + 
              ggtitle("If consume high-calorie food")

plot.count 
```
most people eat high-calorie food.



### Frequency of eating vegetables
never  = 0
sometimes = 1
always = 2
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= vegetables, fill = obe_level )) + 
  geom_bar() + 
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  ggtitle("Frequency of eating vegetables")
plot.count 
```


### Number of main meals
1 = between 1 and 2, 
2 = three, 
3 = more than three, 
4 = no answer
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= num_meals, fill = obe_level )) + 
  geom_bar() + 
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  ggtitle("Number of main meals")
plot.count 
```

most people have more than 3 main meals.



### If eat any food between meals
no = 0
sometimes = 1
frequently = 2
always = 3
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= betw_meals, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank())+
  ggtitle("Frequency of eating food between meals")
plot.count 

```
most people sometimes eat food between meals

### If smoke
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= smoke, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank())+
  ggtitle("Smoke")

plot.count 

```
most of the people don't smoke




### How much water do you drink daily?
less than 1 L = 0
between 1 and 2L =1
more than 2L = 2

```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= num_water, fill = obe_level )) + 
              geom_bar() +
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  ggtitle("How much water do you drink daily?")

plot.count 

```

### Do you monitor the calories you eat daily?
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= monitor_cal, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  ggtitle("Do you monitor the calories you eat daily?")

plot.count 

```
most of the people don't monitor their calories that they eat every day.



### How often do you have physical activity?
I do not have = 0
1 or 2 days = 1
2 or 4 days =2
4 or 5 days =3
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= num_exercise, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  ggtitle("How often do you have physical activity?")

plot.count 

```
About half of the people don't do physical activity.


### How much time do you use electronic devices such as cell phone, videogames, television, computer and others?
0-2 hours = 0
3-5 hours = 1
more than 5 hours = 2
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= time_devices, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  ggtitle("How much time do you use electronic devices?")
plot.count 
      
```
most of the people use 0-2 hours electronic device


### how often do you drink alcohol?
no = 0
sometimes = 1
frequently = 2
always = 3
```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= num_alcohol, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  ggtitle("how often do you drink alcohol?")

plot.count 

```

most of people drink alcohol sometimes.



### transportation

bike = 0
motorbike = 1
automobile= 2
public transportation = 3
walking =  4

```{r}
plot.count <- ggplot(data = obesity, mapping = aes(x= transportation, fill = obe_level )) + 
              geom_bar() + 
              theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  ggtitle("Mode of transportation")
             

plot.count
              
```

Most of the people use public transportation.


### Relationship between time devices and age
```{r}
ggplot(obesity, aes(x = age,y = time_devices, color = obe_level)) + 
  geom_point(size = 2, alpha = 0.6) +
  labs(x = "age",y = "time devices") + 
  ggtitle("Relationship between time devices and age") 
```



as we can see that time deceives and age have a negative relationships.


From the graphs that generated by the exploratory analysis, 3 main points can be concluded, 
1.  the the distribution of men and women in this dataset is more evenly balanced,both being in the age range of 20-25 years old.
2.  obesity is very easily affected by family obesity history.
3.  the younger the person is, the longer the use of electronic devices is.




## Modeling with tidymodels
 
```{r}
 cols <- c("gender","fam_history", "eat_highcal",  "betw_meals", "smoke", "monitor_cal", "num_exercise", "time_devices", "num_alcohol", "transportation", "vegetables", "num_meals", "num_water")

for (i in cols){
  obesity[,i] <- as.integer(unlist(obesity[,i]))
}
```




```{r}
str(obesity)
```







### Split dataset

```{r}
if (!require('tidymodels')) install.packages('tidymodels'); library('tidymodels')

tidymodels_prefer()
set.seed(123)


data_split <- initial_split(obesity,prop = 0.7, strata = obe_level)

data_split
```




```{r}
train_data <- training(data_split)
test_data <- testing(data_split)

head(train_data)
```


### Visually check the two sets
```{r}
plot_train <- ggplot(train_data, aes(x = 1, fill = obe_level)) +
  geom_bar() +
  theme(axis.title.x = element_blank(), axis.ticks.x = element_blank(),  axis.text.x = element_text(colour = "white"), axis.title.y = element_blank()) +
  theme(legend.position = "none") +
  coord_cartesian(ylim = c(0, 1500)) +
  ggtitle("train set")

plot_test <- ggplot(test_data, aes(x = 1, fill = obe_level)) +
  geom_bar() +
  theme(axis.title.x = element_blank(), axis.ticks.x = element_blank(),  axis.text.x = element_text(colour = "white"), axis.title.y = element_blank()) +
  #theme(legend.position = "none") +
  coord_cartesian(ylim = c(0,1500)) +
  ggtitle("test set")

plot_grid(plot_train, plot_test, align = "v", rel_widths = c(1, 1.25))
```






### Train multiple models

#### Use the grahical interface to select models
```{r}

if (!require('shiny')) install.packages('shiny'); library('shiny')
if (!require('miniUI')) install.packages('miniUI'); library('miniUI')
if (!require('rstudioapi')) install.packages('rstudioapi'); library('rstudioapi')

#parsnip_addin()
```

```{r}

if (!require('discrim')) install.packages('discrim'); library('discrim')
if (!require('ranger')) install.packages('ranger'); library('ranger')
if (!require('nnet')) install.packages('nnet'); library('nnet')
if (!require('e1071')) install.packages('e1071'); library('e1071')
```



### Create recipes to specify model formula and preprocessing

step_dummy() will create "dummy" variables for discrete variables
step_zv() will remove those  variables that contain only a single value
```{r}
obesity_recipe_1 <- 
  recipe(obe_level ~ gender + age + height + weight + fam_history + eat_highcal + vegetables + num_meals + betw_meals + smoke + num_water +monitor_cal + num_exercise + time_devices + num_alcohol + transportation ,data = obesity) %>% 
  step_dummy(all_nominal_predictors(),-obe_level) %>% 
  step_zv(all_predictors())


obesity_recipe_2 <- 
  recipe(obe_level ~ gender + age + height + weight + fam_history + eat_highcal + num_meals + betw_meals + num_exercise  + smoke + monitor_cal + transportation ,data = obesity) %>% 
  step_dummy(all_nominal_predictors(),-obe_level) %>% 
  step_zv(all_predictors())

```



#### Specify the models

decision tree
random forest
Multinomial Logistic Regression
naive Bayes
support vector machine

```{r}


decision_tree_rpart_spec <-
  decision_tree(min_n = 5) %>%
  set_engine('rpart') %>%
  set_mode('classification')

rand_forest_randomForest_spec <-
  rand_forest() %>%
  set_engine('randomForest') %>%
  set_mode('classification')

multinom_reg_nnet_spec <-
  multinom_reg() %>%
  set_engine('nnet') %>% 
  set_mode('classification')


naive_Bayes_naivebayes_spec <-
  naive_Bayes() %>%
  set_engine('naivebayes') %>% 
  set_mode('classification')

svm_linear_kernlab_spec <-
  svm_linear() %>%
  set_engine('kernlab') %>%
  set_mode('classification')



```



#### Use tidymodels to create a workflow
```{r}
obesity_wflow <- 
  workflow_set(preproc = list(all_features = obesity_recipe_1, smaller_set = obesity_recipe_2),
               models = list(dtree = decision_tree_rpart_spec,
                             multilogit = multinom_reg_nnet_spec, 
                             rforest = rand_forest_randomForest_spec,
                             naiveBayes = naive_Bayes_naivebayes_spec,
                             svm = svm_linear_kernlab_spec
                             )) %>% 
  option_add(id = "formula_cart", control = control_grid(extract = function(x) x))

obesity_wflow
```


we create a cross-validated folded objects (folds) for model evaluation.
The training data (train_data) is divided into 5 parts.

```{r}
folds <- rsample::vfold_cv(train_data,v=10)
```


The entire workflow was fitted on each fold of the cross-validation using the workflow_map() function
```{r}
obesity_wflow <- obesity_wflow %>% 
  workflow_map(resamples = folds, fn = "fit_resamples", verbose = TRUE)
```

 rank the results
```{r}
rank_results(obesity_wflow,rank_metric = "roc_auc")
```


```{r}
autoplot(obesity_wflow, metric = "roc_auc")
```



### Fit optimal model

```{r}
obesity_wflow_optimal <- 
  workflow() %>% 
  add_model(multinom_reg_nnet_spec) %>% 
  add_recipe(obesity_recipe_2)

```



```{r}
obesity_fit <- 
  obesity_wflow_optimal %>% 
  fit(data = train_data)  

```


the most important variable
```{r}
obesity_fit %>% 
  extract_fit_engine() %>% 
  varImp()
```


### Predict the test set

We can predict the results of the test set. We predict both probabilities and classes

```{r}
obesity_ranforest_pred <- test_data %>% 
  select(obe_level) %>% 
  bind_cols(predict(obesity_fit, new_data = test_data, type = c("prob")),
            predict(obesity_fit, new_data = test_data, type = c("class"))
            )

obesity_ranforest_pred
```

### Evaluate the model's performance

ROC area under the curve (AUC)
```{r}
roc_auc(obesity_ranforest_pred, truth = obe_level, c(".pred_Underweight", 
                                                     ".pred_Normalweight", 
                                                     ".pred_Overweight", 
                                                     ".pred_Obesity_I",
                                                     ".pred_Obesity_II",
                                                     ".pred_Obesity_III"))
```
Multi-class ROC Curve

```{r}
obeisty_scores <- obesity_fit %>%
  predict(test_data, type = 'prob')
```


```{r}
library(fastDummies)
obeisty_dummy <- dummy_cols(test_data$obe_level)

colnames(obeisty_dummy) <- c('obsity', 'Underweight', 'Normalweight', 'Overweight','Obesity_I','Obesity_II','Obesity_III')
obeisty_dummy <- subset(obeisty_dummy, select = -c(obsity))
```


```{r}
obesity_togeter <- cbind(obeisty_scores, obeisty_dummy)
```


```{r}
obesity_togeter$Underweight <- as.factor(obesity_togeter$Underweight)
roc_Underweight <- roc_curve(data = obesity_togeter, Underweight, .pred_Underweight)
roc_Underweight$specificity <- 1 - roc_Underweight$specificity
colnames(roc_Underweight) <- c('threshold', 'tpr', 'fpr')
auc_Underweight <- roc_auc(data = obesity_togeter, Underweight, .pred_Underweight)
auc_Underweight <- auc_Underweight$.estimate
Underweight <- paste('Underweight (AUC=',toString(round(1-auc_Underweight,2)),')',sep = '')
```


```{r}
obesity_togeter$Normalweight <- as.factor(obesity_togeter$Normalweight)
roc_Normalweight <- roc_curve(data = obesity_togeter, Normalweight, .pred_Normalweight)
roc_Normalweight$specificity <- 1 - roc_Normalweight$specificity
colnames(roc_Normalweight) <- c('threshold', 'tpr', 'fpr')
auc_Normalweight <- roc_auc(data = obesity_togeter, Normalweight, .pred_Normalweight)
auc_Normalweight <- auc_Normalweight$.estimate
Normalweight <- paste('Normalweight (AUC=',toString(round(1-auc_Normalweight,2)),')', sep = '')
```


```{r}
obesity_togeter$Overweight <- as.factor(obesity_togeter$Overweight)
roc_Overweight <- roc_curve(data = obesity_togeter, Overweight, .pred_Overweight)
roc_Overweight$specificity <- 1 - roc_Overweight$specificity
colnames(roc_Overweight) <- c('threshold', 'tpr', 'fpr')
auc_Overweight <- roc_auc(data = obesity_togeter, Overweight, .pred_Overweight)
auc_Overweight <- auc_Overweight$.estimate
Overweight <- paste('Overweight (AUC=',toString(round(1-auc_Overweight,2)),')', sep = '')
```


Obesity_I 
```{r}
obesity_togeter$Obesity_I <- as.factor(obesity_togeter$Obesity_I)
roc_Obesity_I <- roc_curve(data = obesity_togeter, Obesity_I, .pred_Obesity_I)
roc_Obesity_I$specificity <- 1 - roc_Obesity_I$specificity
colnames(roc_Obesity_I) <- c('threshold', 'tpr', 'fpr')
auc_Obesity_I<- roc_auc(data = obesity_togeter, Obesity_I, .pred_Obesity_I)
auc_Obesity_I <- auc_Obesity_I$.estimate
Obesity_I <- paste('Obesity_II (AUC=',toString(round(1-auc_Obesity_I,2)),')', sep = '')
```

```{r}
obesity_togeter$Obesity_II <- as.factor(obesity_togeter$Obesity_II)
roc_Obesity_II <- roc_curve(data = obesity_togeter, Obesity_II, .pred_Obesity_II)
roc_Obesity_II$specificity <- 1 - roc_Obesity_II$specificity
colnames(roc_Obesity_II) <- c('threshold', 'tpr', 'fpr')
auc_Obesity_II<- roc_auc(data = obesity_togeter, Obesity_II, .pred_Obesity_II)
auc_Obesity_II <- auc_Obesity_II$.estimate
Obesity_II <- paste('Obesity_II (AUC=',toString(round(1-auc_Obesity_II,2)),')', sep = '')
```


```{r}
obesity_togeter$Obesity_III <- as.factor(obesity_togeter$Obesity_III)
roc_Obesity_III <- roc_curve(data = obesity_togeter, Obesity_III, .pred_Obesity_III)
roc_Obesity_III$specificity <- 1 - roc_Obesity_III$specificity
colnames(roc_Obesity_III) <- c('threshold', 'tpr', 'fpr')
auc_Obesity_III<- roc_auc(data = obesity_togeter, Obesity_III, .pred_Obesity_III)
auc_Obesity_III <- auc_Obesity_III$.estimate
Obesity_III <- paste('Obesity_III (AUC=',toString(round(1-auc_Obesity_III,2)),')', sep = '')
```


```{r}


if (!require('plotly')) install.packages('plotly'); library('plotly')

fig <- plot_ly()%>%
  add_segments(x = 0, xend = 1, y = 0, yend = 1, line = list(dash = "dash", color = 'black'), showlegend = FALSE) %>%
  add_trace(data = roc_Underweight,x = ~fpr, y = ~tpr, mode = 'lines', name = Underweight, type = 'scatter')%>%
  add_trace(data = roc_Normalweight,x = ~fpr, y = ~tpr, mode = 'lines', name = Normalweight, type = 'scatter')%>%
  add_trace(data = roc_Overweight,x = ~fpr, y = ~tpr, mode = 'lines', name = Overweight, type = 'scatter')%>%
  add_trace(data = roc_Obesity_I,x = ~fpr, y = ~tpr, mode = 'lines', name = Obesity_I, type = 'scatter')%>%
  add_trace(data = roc_Obesity_II,x = ~fpr, y = ~tpr, mode = 'lines', name = Obesity_II, type = 'scatter')%>%
  add_trace(data = roc_Obesity_III,x = ~fpr, y = ~tpr, mode = 'lines', name = Obesity_III, type = 'scatter')%>%
  plotly::layout(xaxis = list(title = "False Positive Rate"), 
         yaxis = list(title = "True Positive Rate"),
         legend = list(x = 100, y = 0.5))
fig
```

Accuracy and others
```{r}
classification_metrics <- metric_set(accuracy, precision, recall,f_meas)

classification_metrics(obesity_ranforest_pred, truth = obe_level, estimate = .pred_class)
```
```{r}
w <- train_data %>% 
  select(obe_level) %>% 
  bind_cols(predict(obesity_fit, new_data = train_data, type = c("prob")),
            predict(obesity_fit, new_data = train_data, type = c("class"))
            )

w
```




```{r}
x <- classification_metrics(w, truth = obe_level, estimate = .pred_class)
x
```

And the confusion matrix

```{r}
conf_mat(obesity_ranforest_pred,truth = obe_level, estimate = .pred_class)
```

```{r}

library(openxlsx)
excel_file <- "..."

write.xlsx(obesity, excel_file)
```



```{r}
saveRDS(obesity_fit,"...")
```


```{r}
a <- as.vector(train_data[291,])

b <- c(1, 22, 1.78, 50, 2, 2, 3, 2, 2,3,1,1)

b_df <- data.frame(
  gender = b[1], 
  age = b[2],
  height = b[3],
  weight = b[4],
  fam_history = b[5],
  eat_highcal = b[6],
  num_meals = b[7],
  betw_meals = b[8],
  num_exercise = b[9],
  transportation = b[10],
  smoke = b[11],
  monitor_cal = b[12]

)

```

```{r}
str(b)
```

```{r}
predict(obesity_fit, b_df, type = "prob")
```




















